|

### 2021-08-06 03-Chp-Systematic-Review.Rmd
End of day:

A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020]

@@

This systematic review was performed in conjunction with a team of secondary reviewer, all of whom . These included Alexandra MacAleenana, Athena Sheppard, Matthew Lee and Lena Schmidt.

@@

The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University). We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

@@

 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

Records were imported into Endnote and deduplicated using the method outlined in Bramer et al. (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g. those matched based on the "Title" field alone).

@@

#### Converting between different

Include formulae and informed assumptions

@@

WHile the analysis of change scores is feasible, as they were explicityl

@@

@@

In addition,

@@

Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)

This tool grew out of a collaboration with other reserachers to design a modular method for creating these plots <!-- Apparently collaboration is a big thing they want to see -->

A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using

Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).

Also, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a

As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.

@@

### Assessment of added value of including preprint

Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
s
Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.

@@

### Deviations from the protocol

A dose response meta-analysis was not planned, marking a departure from the registered protocol. <!-- TODO Check this is accurate -->

Similarly, there was initially no intention to try and examine the risk of bias due to missing evidence.

@@

Straight-forward random effects meta-analysis of binary exposures

```{r primaryFigures, include = FALSE}

<!----------------------------------------------------------------------------->
(ref:fpStatins-cap) __Forest plot showing effect of statins:__

@@

### Triangualtion across evidence sources

### Added evidental value of including preprints {sys-rev-including-preprints}

@@

@@

@@

@@

@@

As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses, predominantly preprinted vs published. Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.

The added evidential value of including these preprints was highlighted in Section \ref()

@@

### Strenghts and limitations

@@

-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.

@@

@@

@@

#### Inclusion of preprints

Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g. they would not have been captured by the search for published papers)

### Use in other chapters

@@

Findings from this review are used though out the subsequent chapters.

For example,

In this chapter I have

This work built on the tool introduced in the preceeding chapter, and the results from the systematic review are used in further chapters.

In Chapter \@ref(cprd-analysis-heading), 
A summary of the evidence guided the

In Chapter \@ref(ipd-heading),

>>>>

A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.

@@

This systematic review was performed in conjunction with a team of secondary reviewer, These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt.

@@

The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University). I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials. As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).

@@

Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal. I also searched bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

@@

Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al. (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g. those matched based on the "Title" field alone).

@@

#### Converting between different exposure measures

<!-- TODO Include formulae and informed assumptions  -->

@@

While the analysis of change scores is feasible, as they were explicityl

@@

This additional appraisal marks a departure from the protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence. This is because the tool did not exist when the protocol was originally registered.

@@

In addition, I where available, I presented results stratified by sex and age.

@@

Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication). This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.^[https://github.com/mcguinlu/robvis/issues/102] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.

Additionally, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a systematic review.<!-- TODO CITATION NEEDED --> As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.

@@

#### Assessment of added value of including preprints

Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew

Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.

@@

@@

Straight-forward random effects meta-analysis of binary exposures, using study defined meaures of each.

<!----------------------------------------------------------------------------->
```{r primaryFigures, include = FALSE}
```

(ref:fpStatins-cap) __Forest plot showing effect of statins:__

@@

<!----------------------------------------------------------------------------->
(ref:funnelStatinsAny-cap) Funnel plot of results examining the relationship between statins and any dementia

(ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/funnel_statins_any.png"))
```
<!----------------------------------------------------------------------------->

### Added evidental value of including preprints {#sys-rev-including-preprints}

@@

As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching, was not substantial (bioRxiv = , medRxiv = ) .

However, this is largely due to the timing of the preprint searches

Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.

This does speak to the over-representation of certain study designs in the preprint literature

Regardless, some studies were identified

@@

### Triangulation across evidence sources

@@

#### Protocol registration

While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecodotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited. In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).

#### Workload

@@

#### People management

@@

As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses (preprinted vs. published). Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.

The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints).

@@

<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->

#### Strengths

@@

-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted. <!-- TODO Though this could -->

@@

<!-- TODO Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g. they would not have been captured by the search for published papers) -->

@@

However, this review also has several limitations.

@@

@@

In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.

This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref()

### 2021-08-06 front-and-back-matter/99-appendices.Rmd
End of day:

This thesis was written in RMarkdown. Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]

All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

>>>>

```{r, include = FALSE}
knitr::write_bib(c(.packages(), "bookdown", "knitr"), here::here("bibliography/packages.bib"))
```

This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

### 2021-08-06 index.Rmd
End of day:

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy in Population Health Sciences
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

#######################
## bibliography path ##
#######################
bibliography: 
    - "bibliography/references.bib"
csl: bibliography/nature.csl
bibliography-heading-in-pdf: Bibliography

>>>>

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy
degreedate: 2022
word-count: |
  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last()`
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
covidStatment: |
  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

#######################
## bibliography path ##
#######################
bibliography: [bibliography/references.bib, bibliography/packages.bib]
csl: bibliography/nature.csl
bibliography-heading-in-pdf: Bibliography
